How cryptic is cryptic diversity? Machine learning approaches to classifying morphological variation in the Pacific Pond Turtle (\textit{Emys marmorata})

### 2016-04-05 doc/draft_turtle.tex
fixed methods for digitzation analysis

We estimated the possible effect of digitization error CITATIONS on our results by comparing within (replicated) specimen Procrustes distances to the distances between classification scheme centroids. 10 randomly selected specimen both for this study and an additional four times. These 50 landmark configurations were then Procrustes superimposed. A range of four Procrustes distances were then calculated as the distance between the original configutation and each replicate configuration. These distances were then compared to the Procrustes distances between the centroids of the different classification schemes of \textit{E. marmorata} being analyzed.

>>>>

We estimated the possible effect of digitization error CITATIONS on our results by comparing within (replicated) specimen Procrustes distances to the distances between classification scheme centroids. 10 randomly selected specimen both for this study and an additional four times. These 50 landmark configurations were then Procrustes superimposed. A range of four Procrustes distances were then calculated as the average of the pairwise distances between each of the replicate configurations. These distances were then compared to the average pairwise Procrustes distance between the class centroids for each classification schemes of \textit{E. marmorata} being analyzed.
